Irt plot extra

### 2022-03-27 manuscript.Rmd
EFA plot correlctly referenced

Table 1 summarizes the survey participants' demographic characteristics. Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses. (XX??) participants were excluded from analysis due to not passing at least one of the "attention check" items. For EFA, a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]. To assess sampling adequacy for CFA, we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per item is required to earn trustworthiness of the result. Both our EFA and CFA sample size exceeded these requirements.
We collected data from `r nrow(num.countries)` countries (`r nrow(numUTC)` time zones).Participants reported a diverse range of geographic location
Participants indicated filling out the online survey from a diverse range of geographic locations. For a complete list of geographic locations, see Suppl. Table \@ref(tab:tztable).

@@

Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy using the EFA sample (n =`r nrow(EFA.data)` [@kaiserIndexFactorialSimplicity1974] . The overall KMO vale for 48 items was `r printnum(KMO$MSA)` which was above the cutoff value (.50) indicating adequate sample size [@hutchesonMultivariateSocialScientist1999].  Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001 indicated the correlations between items are adequate for conducting the EFA. However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than |.30|. The inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`. Figure \@ref(fig:efa-plot-print A) depicts the correlation matrix.

@@

Scree plot ( Figure \@ref(fig:efa-plot-print) B) suggested a six-factor solution. However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (**Supplementary Table 2**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:efa-plot-print) D) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.

@@

With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items. (cross-loading items and poor factor loading (<.30) items). Finally, a five-factor EFA solution with 25 items was accepted with all factor-loading higher than .30 and no cross-loading greater than .30. We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (**Supplementary Table 3**). Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients. The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`. However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:efa-plot-print)(D)) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring. [@desjardinsHandbookEducationalMeasurement2018]. Subsequently, we fitted a six-factor solution. However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (**Supplementary Table 4**).

>>>>

Table 1 summarizes the survey participants' demographic characteristics. Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses. (XX??) participants were excluded from analysis due to not passing at least one of the "attention check" items. For EFA, a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]. To assess sampling adequacy for CFA, we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per item is required to earn trustworthiness of the result. Both our EFA and CFA sample size exceeded these requirements.
We collected data from `r nrow(num.countries)` countries (`r nrow(numUTC)` time zones).Participants reported a diverse range of geographic location
Participants indicated filling out the online survey from a diverse range of geographic locations. For a complete list of geographic locations, see **Supplementary Table 2**.

@@

Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy using the EFA sample (n =`r nrow(EFA.data)` [@kaiserIndexFactorialSimplicity1974] . The overall KMO vale for 48 items was `r printnum(KMO$MSA)` which was above the cutoff value (.50) indicating adequate sample size [@hutchesonMultivariateSocialScientist1999].  Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001 indicated the correlations between items are adequate for conducting the EFA. However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than |.30|. The inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`. Figure \@ref(fig:efa-plot-print)A depicts the correlation matrix.

@@

Scree plot ( Figure \@ref(fig:efa-plot-print)B) suggested a six-factor solution. However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (**Supplementary Table 3**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:efa-plot-print)C) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.

@@

With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items. (cross-loading items and poor factor loading (<.30) items). Finally, a five-factor EFA solution with 25 items was accepted with all factor-loading higher than .30 and no cross-loading greater than .30. Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients. The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`. However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:efa-plot-print)D) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring. [@desjardinsHandbookEducationalMeasurement2018]. Subsequently, we fitted a six-factor solution. However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (**Supplementary Table 4**).
